---
title: "Covariate Selection for the ACT TRAP Mobile Monitoring Campaign"
output: html_document
---
Summary 

* drop irrelevant covariates from the mobile monitoring data 
	* old population density estimates. using 2010 estimates only. 
	+ dropped 'LU' data and kept RLU, since LU covariates are from older aerial photography data from 1970-1980, while RLU covariates are from more current, 2006 satellite data 


* transform and generate new variables for the monitoring and all other relevant data (agency sites, cohort sites), .  
	+ log transformed proximities variables  
	  -	TRAP tends to exponentially decays with increasing distance from the source    
  + created some new proximity variables (e.g. distance to a123)
  + calculate mean columnar NO2 (no_behr) for the years 2005-2007


* prepare for validation by splitting the monitoring data into a training and test set.   

* with the monitoring training data, conduct some initial variable selection to help improve the PLS model fit later:     
  + common.value: excluded variables which have less than 40% [old approach: 20%] of being different from the most common value in monitoring data
	  - eliminates variables with little variability that are not likely to improve (or even worsen) the model fit   
	+ low.landuse:  excluded varilabies with maximum land use variables less than 20 [old approach: 10] in monitoring data
	  - this land use is a small fraction and likely to not have a significant impact relative to everything else in within a buffer    
	+ outlier: excluded variables with outliers more than 2% in monitoring data [NOT doing: and cohort data combined]
	  -	variables may worsen model fit  
  + dropped variables with zero variability within a given route

	



* not doing here
	+ sd.ratio: excluded variables with SD of cohort data greater than 5 times of SD of monitoring data
	  -	drops variables whose distribution is very different in the ACT cohort than the monitoring region in an effort to reduce model extrapolation later on   


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      cache=F, cache.comments = F, 
                      message = F, warning = F, 
                      tidy.opts=list(width.cutoff=60), tidy=TRUE,
                      fig.height = 8, fig.width = 8
                      )  

# Clear workspace of all objects and unload all extra (non-base) packages
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
      detach, character.only=TRUE, unload=TRUE, force=TRUE))
}

pacman::p_load(tidyverse,
               kableExtra,
               sf
               )  

set.seed(1)

```

```{r}
#route info
routes <- readRDS(file.path("..", "..", "2. Prediction Models", "prediction_models_R", "Output", "stops_with_time_vars.rda")) %>%
  mutate(route = as.integer(substr(runname, nchar(runname), nchar(runname)))) %>%
  distinct(route, location)


# import route data, monitoring data & drop irrelevant covariates 
mm0 <- routes %>%
  left_join(read.csv(
    file.path("..", "..", "1. Our Campaign", "Our Campaign R", "Data", "Original", "Geocovariates", "dr0311_mobile_covars.csv"
      #"~", "OneDrive - UW", "Documents","School","PhD", "Dissertation", "TRAP R Project", "Data", "Aim 2", "Geocovariates", "201002", "dr0311_mobile_covars.csv"
      )), by = c("location" = "native_id")) %>%
  # drop empty covariates  
  select_if(~!all(is.na(.))) %>%
  #drop Roosevelt garage & stop w/ 1 obeservation that was replaced by MS0601
  filter(!location %in% c("MS0000", "MS0398")) %>%
  #rearrange columns
  select(location, route, longitude, latitude, contains("lambert"), everything(), 
         # drop older covariates
         -contains(c("pop90_", "pop_")), -starts_with("lu_"),
         #don't need these
         -c(starts_with(c("location_", "block", "tract", "msa", "region"))))  

# save location lat/long
saveRDS(select(mm0, route, location, latitude, longitude#, lambert_x, lambert_y
               ), file.path("Output", "location_lat_long.rda"))

```

* transform and generate new variables for the monitoring and all other relevant data (agency sites, cohort sites), .  
	+ log transformed proximities variables  
	  -	TRAP tends to exponentially decays with increasing distance from the source    
  + created some new proximity variables (e.g. distance to a123)


```{r}
# Fns to generate new variables for all datasets 

# fn returns variable for sum of a2 and a3 roads in each buffer

combine_a23_ll <- function(df) {
  #find buffers for a2-3 length variables
  buffers <- str_subset(names(df), "ll_a[2:3]") %>% str_extract("s[0:9].*")
  
  #for each buffer, calculate sum of a2+a3 length
  for (i in seq_along(buffers)) {
    #i=1
    old_vars <- paste0(c("ll_a2_", "ll_a3_"), buffers[i])
    new_var <- paste0("ll_a23_", buffers[i])
    
    df[new_var] <- apply(df[old_vars], 1, sum)
  }
  return(df)
  }


# fn transform and generate new variables for the monitoring and all other relevant data (agency sites, cohort sites), .  
# 	+ log transformed proximities variables  
#   + created some new proximity variables (e.g. distance to a123), including using combine_a23_ll() fn
#   + calculates average no2_behr (columnar NO2 from 2005-2007)

generate_new_vars <- function(df) {
  
  no2_behr_vars <- c("no2_behr_2005","no2_behr_2006", "no2_behr_2007")
  
  df <- df %>%  
  rowwise() %>%
  mutate(m_to_a123 = min(m_to_a1, m_to_a2, m_to_a3),
         m_to_a23 = min(m_to_a2, m_to_a3),
         
         no2_behr = mean(!!as.symbol(no2_behr_vars))
         ) %>%
    select(-no2_behr_vars) %>%
    ungroup() %>%
    #make min distance 1 m before log transforming
    mutate_at(vars(starts_with("m_to_")), ~ifelse(.==0, 1, .) %>% log(.)) %>%
    rename_at(vars(starts_with("m_to_")), ~gsub("m_to_", "log_m_to_", .)) %>%
    # calculate sum of a2 and a3 roads in each buffer
    combine_a23_ll()
}

 
# test <- generate_new_vars(mm0)
# test %>% select(location, contains("no2_behr")) %>% head(3)

```



```{r}
mm <- generate_new_vars(mm0)
covar_names <- select(mm, log_m_to_a1:last_col()) %>% names() 

#348 initial covariates
print(paste("there are", length(covar_names), "initial covariates"))

```



* randomly split the monitoring data into a training and a test set.   

```{r}
seed_n <- 1111#1989
set.seed(seed_n)

mm_train0 <- slice_sample(mm, prop = 0.9)
mm_test <- anti_join(mm, mm_train0, messages="silent")

saveRDS(mm_test, file.path("Output", "mm_cov_test_set.rda"))

```

```{r, eval=T}
# plot test sites
project_crs <- 4326  #lat/long
#m_crs <- 32148

monitoring_region <- readRDS(file.path("..", "..", "1. Our Campaign", "Our Campaign R", "Data", "Output", "GIS", 
                                       #"monitoring_area_shp.rda"
                                       "monitoring_land_shp.rda"
                                       )) #%>% st_transform(m_crs)

ggplot() +
  geom_sf(data=monitoring_region) +
  geom_sf(data = st_as_sf(mm_train0, coords = c("longitude", "latitude"), crs =  project_crs), aes(col="train")) +
  geom_sf(data=st_as_sf(mm_test, coords = c("longitude", "latitude"), crs =  project_crs), aes(col="test")) +
  labs(title = "Training and test sites",
       subtitle = paste0("set.seed(", seed_n, ")"),
       col = "sites"
       )

```



* with the training data, conduct variable selection to help improve the PLS model fit later:     
  + common.value: excluded variables which have less than 40% of being different from the most common value in monitoring data
	  - eliminates variables with little variability that are not likely to improve (or even worsen) the model fit   
	+ low.landuse:  excluded varilabies with maximum land use variables less than 20% in monitoring data
	  - this land use is a small fraction and likely to not have a significant impact relative to everything else in within a buffer    
	+ outlier: excluded variables with outliers more than 2% in monitoring data [NOT doing: and cohort data combined]
	  -	variables may worsen model fit   
	
```{r}
# functions 

# mon.data = mm_train0
# vars.all = covar_names
# x = mon.data$log_m_to_a1

fail_most_common_value <- function(mon.data, vars.all, common_value_thres = 0.4#0.2
                                   ) {
  
  fail <- apply(mon.data[,vars.all], 2, function(x) {
    y <- table(x) 
    mode_val <- as.numeric(names(y)[y==max(y)])
    sum(x != mode_val)/length(x) < common_value_thres
    }
    ) %>%
    as.data.frame() %>%
    filter(.==TRUE) %>%
    rownames()
  
  return(fail)
  }


fail_low_landuse <- function(mon.data, vars.all, lowValue=20 #10
                             ) 
{
  lu.vars <- grep("^rlu_|^lu", vars.all, value=T)
  fail <- sapply(lu.vars, function(x) return (max(mon.data[, x]) < lowValue))
  fail <- names(fail)[grep("TRUE", fail)]
  return (fail)
}


# # [ probably dont need this since monitoring stops are similar to the cohort ]
# fail_sd_ratio <- function(mon.data, cohort.data, vars.all, thres=5) 
# {
#   fail <- c()
#   for (i in vars.all)  {
#     #i=vars.all[1]
#     mon.sd <- sd(mon.data[, i], na.rm=TRUE)
#     cohort.sd <- sd(cohort.data[, i], na.rm=TRUE)
#         if (cohort.sd > thres * mon.sd | all(is.na(mon.sd))) 
#       # [ vector of variables where cohort sites are more variable than monitoring sites ]
#       fail <- c(fail, i)
#     
#   }
#   return (fail)
# }

fail_outlier_check <- function(mon.data, #cohort.data, 
                               vars.all, outlier_thres=0.02) 
{
  all.data = rbind(mon.data[,vars.all]#, cohort.data[,vars.all]
                   )
  
  fail <- sapply( vars.all, function(x) 
    return (  sum(abs(scale(all.data[, x]))> 5) > nrow(all.data)*outlier_thres  ) )
  fail <- names(fail)[grep("TRUE", fail)]
  return (fail)
}


```

```{r}
# mon.data = mm_train0
# vars.all = covar_names
# 
# #new variables dropped
# drop_vars[!drop_vars %in% drop_variables]

# variables that still have too little variability by route 
# returns variables with no variability in any single route (for simulations later)
low_sd_by_route <- function(mon.data, vars.all) {
  
  drop_vars <- mon.data %>%
  group_by(route) %>%
  summarize_at(vars(vars.all), ~sd(.)) %>%
  #gather(cov, sd, vars.all) %>%
  pivot_longer(vars.all, names_to = "cov", values_to = "sd") %>%
    
  # covariates with no variation
  filter(sd == 0) %>% 
  distinct(cov) %>% pull()
  
  return(drop_vars)
  
}


```


```{r}
# combine all fns above
drop_variables_fn <- function(monitoring_data, covar_names) {
  result <- list(
    fail_most_common_value_vars = fail_most_common_value(mon.data = monitoring_data, vars.all = covar_names),
    fail_low_landuse = fail_low_landuse(mon.data = monitoring_data, vars.all = covar_names),
    fail_outlier_check = fail_outlier_check(mon.data = monitoring_data, vars.all = covar_names),
    
    low_sd_by_route = low_sd_by_route(mon.data = monitoring_data, vars.all = covar_names)
    )
  
  return(result)
  
}

```

 
```{r}
# variables dropped are the same when restrict to routes 1-3
drop_variables <- drop_variables_fn(monitoring_data = mm_train0, covar_names = covar_names)

drop_variables %>%
  kable(caption = "variables droped becausae of: low variability, low and use, outliers, and zero variability (SD) within any given route, respectively") %>%
  kable_styling()

# for HEI modeling, which is more restrictive
drop_variables <- unlist(drop_variables, use.names = F) %>% unique()
print(paste0(length(drop_variables), " variables were dropped for HEI simulations"))

#for most other modeling
drop_variables_fewer <- unlist(drop_variables[-4], use.names = F) %>% unique()
print(paste0(length(drop_variables_fewer), " variables were dropped for all other prediction modeling"))

# diff # em_CO_s03000 # ????
# setdiff(drop_variables, drop_variables_fewer)
 

#variables to use for HEI modeling
keep_variables <- setdiff(covar_names, drop_variables)
print(paste("There are",length(keep_variables), "variables left for HEI modeling"))

keep_variables %>%
  paste(collapse = ", ") %>%
  kable() %>%
  kable_styling()

#variables to use for all other modeling
print(paste("There are",length(setdiff(covar_names, drop_variables_fewer)), "variables left for all other modeling"))



```



```{r}
#save final training data
## for HEI simulations, which also restrict to low variability by route
select(mm_train0, -drop_variables) %>%
  saveRDS(., file.path("Output", "mm_cov_train_set_hei.rda"))

## for all other models
select(mm_train0, -drop_variables_fewer) %>%
  saveRDS(., file.path("Output", "mm_cov_train_set.rda"))

```


 
